### 2020-03-17 README.Rmd
Changed every instance of timeternR to EpiCompare

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/skgallagher/timeternR.svg?branch=master)](https://travis-ci.org/skgallagher/timeternR)
[![codecov](https://codecov.io/gh/skgallagher/timeternR/branch/master/graph/badge.svg)](https://codecov.io/gh/skgallagher/timeternR)
<!-- badges: end -->

The goal of timeternR is to develop functional based visualization and statistics that focus on use in ternary plots.

@@

You can install the developmental version of timeternR from github using:

``` r
# install.packages("devtools")
devtools::install_github("skgallagher/timeternR")
```

@@

   Currently there are 13 data sets in which to explore the different `timeternR` functions.  These correspond to different sources of raw data along, agent vs. aggregate format, and emphases of different processes such as vital dynamics (e.g. birth and).

@@

```{r message = F, warning = F}
library(tidyverse)
library(ggtern)
library(timeternR)
```
The following example comes from a Measles outbreak in Hagelloch, Germany in 1861. We have data on each child (agent) in the town.
```{r}
hagelloch_raw %>%
  ggplot(aes(y = tI, z = tR)) +
    geom_aggregate() + 
    coord_tern() +
    labs(x = "S", y = "I", z = "R", title = "Town Analysis")
```

@@

## Notes:
1. For writing code that works with `tidyverse` 1.0 vs `tidyverse` <= 0.8.3. We followed ideas found in [tidyr: in-packages](https://tidyr.tidyverse.org/articles/in-packages.html), for the code, and - when working with Travis CI (using a matrix for multiple builds) - we leverage ideas in [tidyverse travis on github](https://github.com/tidyverse/design/issues/95) and [tidyverse principles](https://principles.tidyverse.org/changes-multivers.html).
2. For writing your own `geom`s and `stat`s that works with `ggtern` (which are generally restricted), the following 2 stack-exchange articles helped use do so with ease:
    a. [stack-exchange: personal code idea](https://stackoverflow.com/questions/57175114/ternary-plot-scaling-opacity-across-groups)
    b. [stack-exchange: being able to access ggtern's element write away](https://stackoverflow.com/questions/31589479/how-to-fix-no-item-called-packagepkg-on-the-search-list-without-using-libra#comment51172891_31589479)
    c. Finally, we've also leveraged ideas from [R-devel: on avoiding problems with `:::`](https://stat.ethz.ch/pipermail/r-devel/2013-August/067210.html) in `R/aaa.R` to overcome messages from CRAN relative to this hack (using `:::`). For some reason - when documenting for `pkgdown` website, we need to do `library(ggtern); timeternR:::update_approved_layers()`

>>>>

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/skgallagher/EpiCompare.svg?branch=master)](https://travis-ci.org/skgallagher/EpiCompare)
[![codecov](https://codecov.io/gh/skgallagher/EpiCompare/branch/master/graph/badge.svg)](https://codecov.io/gh/skgallagher/EpiCompare)
<!-- badges: end -->

The goal of EpiCompare is to develop functional based visualization and statistics that focus on use in ternary plots.

@@

You can install the developmental version of EpiCompare from github using:

``` r
# install.packages("devtools")
devtools::install_github("skgallagher/EpiCompare")
```

@@

   Currently there are 13 data sets in which to explore the different `EpiCompare` functions.  These correspond to different sources of raw data along, agent vs. aggregate format, and emphases of different processes such as vital dynamics (e.g. birth and).

@@

```{r message = F, warning = F}
library(tidyverse)
library(ggtern)
library(EpiCompare)
```
The following example comes from a Measles outbreak in Hagelloch, Germany in 1861. We have data on each child (agent) in the town.
```{r}
hagelloch_raw %>%
  ggplot(aes(y = tI, z = tR)) +
    geom_aggregate() + 
    coord_tern() +
    labs(x = "S", y = "I", z = "R", title = "Town Analysis")
```

@@

## Notes:
1. For writing code that works with `tidyverse` 1.0 vs `tidyverse` <= 0.8.3. We followed ideas found in [tidyr: in-packages](https://tidyr.tidyverse.org/articles/in-packages.html), for the code, and - when working with Travis CI (using a matrix for multiple builds) - we leverage ideas in [tidyverse travis on github](https://github.com/tidyverse/design/issues/95) and [tidyverse principles](https://principles.tidyverse.org/changes-multivers.html).
2. For writing your own `geom`s and `stat`s that works with `ggtern` (which are generally restricted), the following 2 stack-exchange articles helped use do so with ease:
    a. [stack-exchange: personal code idea](https://stackoverflow.com/questions/57175114/ternary-plot-scaling-opacity-across-groups)
    b. [stack-exchange: being able to access ggtern's element write away](https://stackoverflow.com/questions/31589479/how-to-fix-no-item-called-packagepkg-on-the-search-list-without-using-libra#comment51172891_31589479)
    c. Finally, we've also leveraged ideas from [R-devel: on avoiding problems with `:::`](https://stat.ethz.ch/pipermail/r-devel/2013-August/067210.html) in `R/aaa.R` to overcome messages from CRAN relative to this hack (using `:::`). For some reason - when documenting for `pkgdown` website, we need to do `library(ggtern); EpiCompare:::update_approved_layers()`
